### 2021-04-12 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Rework objective; add structure overview; some conclusion stuff

\chapter{Introduction}\label{chap:introduction}
Headed by Bitcoin in 2009, ``cryptocurrencies have emerged as the first generation of blockchain technology'' \cite{alharby_blockchain_2017}. However, their transactions are mostly limited to simple monetary transactions or registration of assets or ownerships \cite{alharby_blockchain_2017}. More recent blockchains, considered as the second generation \cite{alharby_blockchain_2017}, aim to provide a platform for building more sophisticated and complex applications on top of the technology. These are built with smart contracts, programs written in Turing-complete languages. Running a smart contract, though, generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{alharby_blockchain_2017}. These fees, often measured in a unit called ``gas'', have to be paid for by the user in order to compensate the miners for their efforts \cite{chen_under-optimized_2020}. This creates a powerful incentive to keep smart contracts simple and efficient, while in effect, meaningful applications still might need to perform some resource intensive computations. Not only can such applications generate unsustainable costs when executed on the blockchain, but they may also reach gas limits imposed by the blockchain's protocol. \\
In order to avoid these costs and restrictions, such an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a smart contract as an input parameter for further processing or recording \cite{thiemann_2020}. By trusting that the submitted results are correct, this approach raises both safety and security issues. Invalid results can be submitted unintentionally as a result of a wrong computation, or a third party may pass them intentionally to cause harm or take advantage. Consequently, submitted parameters should be checked for assumed properties before the smart contract is executed. Although in many cases, verifying a solution takes less time than computing the result itself\footnote{cf. NP-hard problems \cite{nph_problems}, sorting algorithms \cite{review_sorting}\cite{cpp_issorted}, etc.}, the generated costs for checking the validity increase with the size of the input. \\
Consider, for instance, the following contract:
\begin{lstlisting}[caption=Smart contract expecting a prime number \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:prime]
contract Example {
	function ( int p ) public {
	// assume p is prime
	...
	}
}
\end{lstlisting}
The assumption, that the given integer $p$ is a prime, can be expressed as an explicit assertion in predicate logic \cite{thiemann_2020}: 
\begin{equation}\label{eq:prime}
    (\forall n) (2 \le n \le \sqrt{p}) \Rightarrow (p \% n) \neq 0
\end{equation}
To check whether this property holds for $p$, the contract has to execute a loop. Assuming computing the body of the loop takes constant time, this test has a time complexity of $\mathcal{O}(\sqrt{p})$ and therefore generates costs linear in $\sqrt{p}$ on top of the cost for executing the actual contract. Thus, a mechanism is required that allows the smart contract to make use of the result computed by an off-chain source, without having to check its validity locally with scaling costs.

@@

Each validator then checks the inverse property $(p \% n) = 0$ point-wise for some random $n$ within the given boundaries $2 \le n \le \sqrt{p}$. If a validator finds a counterexample, i.e., a value for $n$ where the reminder is $0$, it posts an objection to the network. For each involved validator, the constant cost of generating one random number and calculating one division have to be paid, which is independent from $p$. \\
However, distributed assertion checking is not only applicable for parameters or properties of dynamic size. Another example given in \cite{thiemann_2020} shows a contract that expects an array of integers sorted in ascending order:

\begin{lstlisting}[caption=Smart contract expecting a sorted array, numbers=none, language=Solidity, label=lst:sorted]
contract Sorted {
  function find ( int [50] a , int v ) public {
    // assume a is sorted
  }
}
\end{lstlisting}

@@

Since the validators sample the domain randomly, the absence of a counterexample doesn't prove that the assumption is correct; the validation is only probabilistic and the reliability depends on the number of validators in the network. This corresponds to the principle of Bloom filters, where a queried element is either ``certainly not'' or ``possibly'' a member of a defined set \cite{blustein_bloom_2002}. In the case of assertion checking, we consider the assumption to be either definitely not or possibly valid. The probability of false positives in Bloom filters is an approximate function of the filter size and the number of inserted elements, supposing an optimal number of hash functions have been implemented. Tuning these parameters is a trade-off between making the filter more reliable, i.e., lowering its error rate, and space efficiency \cite{blustein_bloom_2002}. The same applies, with some reservations, to distributed assertion checking: less samples keep the gas consumption to a minimum, whereas more samples increase the probability that an existing counterexample is found. Referring to the example of sorted lists,  the probability of false positives depends on the size of the list $a$ and the number of validators $m$.\\
The importance of the former parameter becomes obvious when looking at the worst case scenario of the same example. Assume the array is unsorted at exactly one position - the probability that the each of the $m$ validators independently check this position is $\frac{1}{|a|}$, while all of them checking any other position $\frac{|a|-1}{|a|}$. If the random generator chooses each value for $n$ independently from a uniform distribution, the probability that the counterexample is not detected by any validator converges to 0 if the number of validators approaches infinity \cite{thiemann_2020}:
\begin{equation}\label{eq:limes_validators}
	\lim_{m\to\infty} \left(\frac{|a|-1}{|a|}\right)^m = 0
\end{equation}

\section{Objective}
This thesis conducts research into the feasibility and performance of the proposed approach and explores possible designs for the implementation of both the necessary off-chain infrastructure and the amendment of the blockchain protocol. To this end, a first approximation of a set of formulas amenable for distributed assertion checking is defined, special cases are identified and, if necessary, excluded. While parts of the offline design and infrastructure should be, in parts, applicable to any blockchain supporting smart contracts, the case example for the protocol-specific parts of the design target the Tezos blockchain and its built-in contract language Michelson. On the basis of the achieved results, the efficiency of the approach is ultimately assessed.

\section{Structure overview}
\draft{Finish when structure \& chapters finalised.}
\begin{itemize}
\item Assessment of use cases for this kind of assertion checking (Chapter 2)
	\begin{itemize}
	\item defines a set of logical formula
	\item gives some useful examples
	\item cost analysis for checking them normally
	\end{itemize}
\item Generic Offline Design (Chapter 3)
	\begin{itemize}
	\item definition of language/syntax to express assertions over given set of logical formulas
	\item formalizes the transformation
	\item describes frontend of pipeline
	\item analyses accuracy of this approach
	\end{itemize}
\item Tezos-specific Offline Design (Chapter 4)
	\begin{itemize}
	\item introduction/Overview to Tezos
	\item necessary extensions to Michelson's instruction set \& evaluator
	\item description of the pipeline backend
	\item Cost analysis \& accuracy on Tezos
	\end{itemize}
\item Conclusion \& outlook
	\begin{itemize}
	\item Next steps/ToDos for development; open issues
	\item Evaluation of costs -> is this approach promising?
	\item Alternatives? E.g. Refer to TrueBit
	\end{itemize}
\end{itemize}

>>>>

\chapter{Introduction}\label{chap:introduction}
Headed by Bitcoin in 2009, ``cryptocurrencies have emerged as the first generation of blockchain technology'' \cite{alharby_blockchain_2017}. However, their transactions are mostly limited to simple monetary transactions or registration of assets or ownerships \cite{alharby_blockchain_2017}. More recent blockchains, considered as the second generation \cite{alharby_blockchain_2017}, aim to provide a platform for building more sophisticated and complex applications on top of the technology. These are built with smart contracts, programs written in Turing-complete languages. Running a smart contract, though, generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{alharby_blockchain_2017}. These fees, often measured in a unit called ``gas'', have to be paid for by the user in order to compensate the miners for their efforts \cite{chen_under-optimized_2020}. This creates a powerful incentive to keep smart contracts simple and efficient, while in reality, meaningful applications still might need to perform some resource intensive computations. Not only can such applications generate unsustainable costs when executed on the blockchain, but may also reach gas limits imposed by the blockchain's protocol. \\
In order to avoid these costs and restrictions, such an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a smart contract as an input parameter for further processing or recording \cite{thiemann_2020}. By trusting that the submitted results are correct, this approach raises both safety and security issues. Invalid results can be submitted unintentionally as a result of a wrong computation, or a third party may pass them intentionally to cause harm or take advantage. Consequently, submitted parameters should be checked for assumed properties before the smart contract is executed. Although in many cases, verifying a solution takes less time than computing the result itself (cf. NP-hard problems \cite{nph_problems} or sorting algorithms \cite{review_sorting}\cite{cpp_issorted}), the generated costs for checking the validity increase with the size of the input. \\
Consider, for instance, the following smart contract:
\begin{lstlisting}[caption=Smart contract expecting a prime number \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:prime]
contract Example {
	function ( int p ) public {
	// assume p is prime
	...
	}
}
\end{lstlisting}
The assumption, that the given integer $p$ is a prime, can be expressed as an explicit assertion in predicate logic \cite{thiemann_2020}: 
\begin{equation}\label{eq:prime}
    (\forall n) (2 \le n \le \sqrt{p}) \Rightarrow (p \% n) \neq 0
\end{equation}
To check whether this property holds for $p$, the contract has to execute a loop. Assuming computing the body of the loop takes constant time, this test has a time complexity of $\mathcal{O}(\sqrt{p})$ and therefore generates costs linear in $\sqrt{p}$ on top of the cost for executing the actual contract. Thus, a mechanism is required that allows the smart contract to make use of the result computed by an off-chain source, without having to check its validity locally with scaling costs.

@@

Each validator then checks the inverse property $(p \% n) = 0$ point-wise for some random $n$ within the given boundaries $2 \le n \le \sqrt{p}$. If a validator finds a counterexample, i.e., a value for $n$ where the reminder is $0$, it posts an objection to the network. For each involved validator, the constant cost of generating one random number and calculating one division have to be paid, which is independent from $p$. \\
However, distributed assertion checking is not only applicable for parameters or properties of dynamic size. Another example is a contract that expects an array of integers sorted in ascending order:

\begin{lstlisting}[caption=Smart contract expecting a sorted array \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:sorted]
contract Sorted {
  function find ( int [50] a , int v ) public {
    // assume a is sorted
  }
}
\end{lstlisting}

@@

Since the validators sample the domain randomly, the absence of a counterexample doesn't prove that the assumption is correct; the validation is only probabilistic and the reliability depends on the number of validators in the network. This corresponds to the principle of Bloom filters, where a queried element is either ``certainly not'' or ``possibly'' a member of a defined set \cite{blustein_bloom_2002}. In the case of assertion checking, we consider the assumption to be either definitely not or possibly valid. The probability of false positives in Bloom filters is an approximate function of the filter size and the number of inserted elements, supposing an optimal number of hash functions have been implemented. Tuning these parameters is a trade-off between making the filter more reliable, i.e., lowering its error rate, and space efficiency \cite{blustein_bloom_2002}. The same applies, with some reservations, to distributed assertion checking: less samples keep the gas consumption to a minimum, whereas more samples increase the probability that an existing counterexample is found. Referring to the example of sorted lists,  the probability of false positives depends on the size of the list $a$ and the number of validators $m$.

The importance of the former parameter becomes apparent when considering the worst case scenario of the same example. Assuming the array is unsorted at exactly one position - the probability that the each of the $m$ validators independently check this position is $\frac{1}{|a|}$, whereas the probability of all of them checking any other position $\frac{|a|-1}{|a|}$. If the random generator chooses each value for $n$ independently from a uniform distribution, the probability that the counterexample is not detected by any validator converges to 0 if the number of validators approaches infinity \cite{thiemann_2020}:
\begin{equation}\label{eq:limes_validators}
	\lim_{m\to\infty} \left(\frac{|a|-1}{|a|}\right)^m = 0
\end{equation}

\section{Objective}
This thesis proposes the portrayed approach of a distributed assertion checking scheme in order to make more efficent use of off-chain resources. The realisation of such assertions consists of two components - the off-chain design and implementation of supporting infrastructure, as well as the extension of the smart contract language and amendment of the blockchain protocol, s.t. these assertions are triggered and handled correctly by the network. The focus of this thesis is put primarily on the off-chain component and the development of a toolchain that transforms and translates assertions to executable code for the target platform, but elaborates on the protocol design where necessary. To this end, a first approximation of a set of formulas amenable for distributed assertion checking is defined, special cases are identified and, if necessary, excluded. While the off-chain design and toolchain should be partially applicable to any blockchain supporting smart contracts, the case example for the protocol-specific parts of the design targets the Tezos blockchain and its built-in contract language Michelson. On the basis of the chosen design, the thesis evaluates the efficiency of the approach in terms of costs incurred by checking a formula on Tezos, and discusses if, and under which conditions, these costs are competitive versus a local approach.

\section{Structure overview}
The structure of this thesis is as follows: in the first instance, \chapref{chap:use_cases} defines a set of logical formulas that describe parameter properties and are suitable for distributed assertion checking. Given this set, it demonstrates various practical use-cases for such properties and formalizes the costs of checking them locally, s.t. they can later be referenced to assess the efficiency of the distributed approach. \chapref{chap:offline} describes the generic aspects of the off-chain design and infrastructure, i.a. the definition of a syntax to express assertions on top of the logical formulas and how they are transformed to code that checks for counterexamples. Additionally, it analyses the effectiveness of the statistical validation for a given input and provides a formula to compute the lower bound of validators necessary to obtain a reliable result. Subsequently, \chapref{chap:offline_tezos} gives a brief introduction to Tezos, before it covers target specific aspects of the off-chain design. Besides identifying necessary extensions to Michelson's instruction set and virtual machine, it explores various orchestration strategies between assertion and contract code. The chapter closes with a cost analysis of distributed assertion checking on Tezos with the chosen orchestration strategy. In conclusion, the last chapter recaps the achieved results, 
addresses any open questions or issues and provides an outlook on upcoming work on this topic.

### 2021-04-12 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Rework objective; add structure overview; some conclusion stuff

\chapter{Generic Offline Design}\label{chap:offline}
The implementation of distributed assertion checking on any blockchain requires some off-chain considerations and infrastructure. The previous chapter defined a formal set of logical formulae amenable for this approach and gave some in-depth examples. As stated before, the proposed implementation in the following chapters is, for the most part, restricted to formulas of predicate logic using universal quantification.\\
The purpose of the offline infrastructure is to provide a syntax for stating assertions that check logical formulas, as well as a toolchain to compile these assertions into code that can be originated on the target blockchain. Depending on the individual solution for the respective blockchain protocol, this can either be the original contract extended directly with the assertion code, or as a separate contract that extends the original contract in some other way. This chapter describes the generic part of the offline design, which corresponds to the frontend of the compilation pipeline shown in \figref{fig:pipeline_frontend}. As a start, \secref{sec:syntax} describes the concrete syntax for writing assertions and shows how it expresses some of the previously given examples. The stages of the pipeline frontend, including parsing and transforming the original assertions to assertions that check for counterexamples, are described in \secref{sec:pipeline_front}. Lastly, \secref{sec:accuracy} analyses the reliability of distributed assertion checking as proposed and the cost incurred by increasing it.

>>>>

\chapter{Generic Off-Chain Design}\label{chap:offline}
The implementation of distributed assertion checking on any blockchain requires some off-chain considerations and infrastructure. The previous chapter defined a formal set of logical formulae amenable for this approach and gave some in-depth examples. As stated before, the proposed implementation in the following chapters is, for the most part, restricted to formulas of predicate logic using universal quantification.\\
The purpose of the off-chain infrastructure is to provide a syntax for stating assertions that check logical formulas, as well as a toolchain to compile these assertions into code that can be originated on the target blockchain. Depending on the individual solution for the respective blockchain protocol, this can either be the original contract extended directly with the assertion code, or as a separate contract that extends the original contract in some other way. This chapter describes the generic part of the off-chain design, which corresponds to the frontend of the compilation pipeline shown in \figref{fig:pipeline_frontend}. As a start, \secref{sec:syntax} describes the concrete syntax for writing assertions and shows how it expresses some of the previously given examples. The stages of the pipeline frontend, including parsing and transforming the original assertions to assertions that check for counterexamples, are described in \secref{sec:pipeline_front}. Lastly, \secref{sec:accuracy} analyses the reliability of distributed assertion checking as proposed and the cost incurred by increasing it.

### 2021-04-12 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Rework objective; add structure overview; some conclusion stuff

\subsubsection{Internal operations}
Smart contracts are able to call other smart contracts by emitting internal operations. The return type of Michelson programs is a tuple of a list of internal operations and the updated storage. Thus, after the actual contract has been executed, the operations of the returned list are run in sequence. Since the internal operations may in turn also emit internal operations, they are put into a queue and are processed in order. As an example, \figref{fig:internal_ops} shows an execution order of two external transactions, i.e., transactions which have been initiated by a user account, and their internal operations.
\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{figures/4-offline_tezos/internal_ops}
\caption{Execution order of two external operations and their internal operations; Source: \cite{tezos_docs}}
\label{fig:internal_ops}
\end{figure}

>>>>

\subsubsection{Internal operations}
Smart contracts are able to call other smart contracts by emitting internal operations. The return type of Michelson programs is a tuple of a list of internal operations and the updated storage. Thus, after the actual contract has been executed, the operations of the returned list are run in sequence. Since the internal operations may in turn also emit internal operations, they are put into a queue and are processed in order. As an example, \figref{fig:internal_ops} shows an execution order of two external transactions in sequence, i.e., transactions which have been initiated by a user account, and their internal operations.
\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{figures/4-offline_tezos/internal_ops}
\captionsource{Execution order of two external operations and their internal operations}{\cite{tezos_docs}}
\label{fig:internal_ops}
\end{figure}

### 2021-04-12 assertions/doc/thesis-bernhardt/chapters/5-conclusion.tex
Rework objective; add structure overview; some conclusion stuff

\chapter{Conclusion and outlook}\label{chap:conclusion}
\draft{}
\begin{itemize}
\item Summarize what has been implemented so far
\item Next steps
	\begin{itemize}
	\item extending VM \& Michelson
	\item compiler
	\item list open questions
	\item Protocol-design
		\begin{itemize}
		\item Do endorsers validate or extra validators?
		\item How to differentiate between SC w/ and w/o assertions?
		\item How to implement the waiting?
		\item Which transactions/messages can be reused or need to be introduced
		\item Representing counterexamples and verifying them
		\item Penalty for incorrect counterexamples
		\end{itemize}
	\end{itemize}
\item Estimation of cost reduction (or increase?)
\item Alternatives (e.g. TrueBit)
\end{itemize}

>>>>

\chapter{Conclusion and outlook}\label{chap:conclusion}
In order to make use of off-chain computations in smart contracts, this thesis proposed an approach that engages the validators of the blockchain network in a distributed effort to check assertions over input parameters. It covered the partially generic off-chain component of the design and implementation of this approach, while also providing some projections and considerations for the Tezos specific protocol design.

As a first step, it identified properties that can be checked with the proposed scheme, represented by a set of formulas in propositional logic using quantification. By means of some practical use-cases, the semantic differences between universal and existential quantification in relation to assertion checking were highlighted, namely that existential quantification requires the validators to find proofs instead of counterexamples. Even though the thesis focused on distributed refutation, distributed verification is a meaningful extension of future work on this topic.

Based on the set of formulas, the generic off-chain design introduced a simple syntax to express assertions for one or more entrypoints of a contract, followed by a formalization of their transformation which comprises the negation of the formula and translation of quantifiers to efficient random generators. After exploring several orchestration strategies of contract and assertion code, the Tezos specific off-chain design proposed to originate the assertion and manager code modularly and discussed the necessary implementations within the off-chain infrastructure and, partially, the protocol design. This off-chain infrastructure was implemented in OCaml in form of a toolchain, which translates a file of assertions to executable smart contracts for the target platform.\\

% paragraph evaluation

%In conclusion, it analysed the cost incurred by checking assertions as proposed and compared the results to a non-distributed approach. Based on these results, thesis discusses alternatives or possible modifications to solve some of the issues at hand. \\

%contains a compilation pipeline written in OCaml that

%An analysis of the general accuracy of the proposed scheme showed that 
% and stating a formula to compute the minimum amount of random checks to reach a certain confidence level,
%- high costs due to several reasons: random checking values require more test runs than size of iteration space. going below n checks does not provide a high certainty over validity. This approach is thus not suitable for safety or security critical applications. 
%- more effort in compilation returns a better cost-performance ratio if the manager contract and assertions are merged. Still, more base costs
%- depends on the protocol design, whether this approach is worth pursuing -> if the cost for validation can be eliminated by using rewards, it might be realisable.
%- quantifiers: other semantics for certain combinations/existentials --> proofs; here not considered, but would be interesting for future work on this topic

\subsection{Outlook}

\draft{}
\begin{itemize}
\item Summarize what has been implemented so far
\item Next steps
	\begin{itemize}
	\item extending VM \& Michelson
	\item compiler
	\item list open questions
	\item Protocol-design
		\begin{itemize}
		\item Do endorsers validate or extra validators?
		\item How to differentiate between SC w/ and w/o assertions?
		\item How to implement the waiting?
		\item Which transactions/messages can be reused or need to be introduced
		\item Representing counterexamples and verifying them
		\item Penalty for incorrect counterexamples
		\end{itemize}
	\end{itemize}
\item Estimation of cost reduction (or increase?)
\item Alternatives (e.g. TrueBit)
\end{itemize}

### 2021-04-12 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Rework objective; add structure overview; some conclusion stuff

\section{\texttt{Foo}}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:foo_manager,
				 caption=Manager contract of \texttt{Foo}]{listings/foo_manager.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:foo_manager,
				 caption=Assertion contract of \texttt{Foo}]{listings/foo_assertion.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:foo_manager,
				 caption=Parent contract of \texttt{Foo}]{listings/foo_parent.tz}

\section{\texttt{Bar}}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:bar_manager,
				 caption=Manager contract of \texttt{Bar}]{listings/bar_manager.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:bar_manager,
				 caption=Assertion contract of \texttt{Bar}]{listings/bar_assertion.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:bar_manager,
				 caption=Parent contract of \texttt{Bar}]{listings/bar_parent.tz}

>>>>

\section{\texttt{Foo}}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:foo_manager,
				 caption=Manager contract of \texttt{Foo}]{listings/foo_manager.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:foo_assertion,
				 caption=Assertion contract of \texttt{Foo}]{listings/foo_assertion.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:foo_parent,
				 caption=Parent contract of \texttt{Foo}]{listings/foo_parent.tz}

\section{\texttt{Bar}}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:bar_manager,
				 caption=Manager contract of \texttt{Bar}]{listings/bar_manager.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:bar_assertion,
				 caption=Assertion contract of \texttt{Bar}]{listings/bar_assertion.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:bar_parent,
				 caption=Parent contract of \texttt{Bar}]{listings/bar_parent.tz}
